Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-27 Ben_Manuscripts/thesis/hdphmm_si.tex
spell checking and mod to usage of subdiffusion

\documentclass{article}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[M-]{Draft}

\title{Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
       of Solute Trajectories in Nanostructured Membranes.}

\author{Benjamin J. Coscia, Christopher P. Calderon \and Michael R. Shirts}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\begin{document}

  \graphicspath{{./supporting_figures/}}
  \maketitle

@@

  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the figures
  that follow, we graphically illustrate the procedure which is described in detail in
  Section~\ref{M-method:IHMM} of the main text.

@@

  \begin{figure}
    \centering
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{xyz_hmm.pdf}
		\caption{}\label{fig:xyz_hmm}
	\end{subfigure}  	
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{rz_hmm.pdf}
		\caption{}\label{fig:rz_hmm}
	\end{subfigure}  
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{zeroed_hmm.pdf}
		\caption{}\label{fig:zeroed_hmm}
	\end{subfigure}  
	\caption{IHMM parameterization is a multi-step procedure. In the above plots, distinct colors
	correspond to distinct state behavior. (a) First we parameterize the trajectories in terms of
	the $x$, $y$, $z$ solute center-of-mass coordinates with the $x$ and $y$ coordinates relative
	to the nearest pore center (b) Next, we convert the $x$ and $y$ 	
	coordinates to radial coordinates, $r$, then fix the state sequence and use the inference 
	component of the IHMM in order to estimate the parameters in terms of $r$ and $z$. Note that
	the segment colors in (b) are the same as (a) because we fixed the state sequence.
	(c) After clustering the VAR parameters and reassigning the state sequence so that segments 
	which belong to the same cluster are labeled the same across all solute trajectories, we subtract
	the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory, and then fix the clustered state sequence to infer the parameters of each clustered 
  	state, assuming a mean of zero for all states. Note that the colors are no longer aligned with 
  	figures (a) and (b) because the states are relabeled in terms of their clusters. There are
  	also less states in this single trajectory.
	}\label{fig:hmm_demo}
  \end{figure}

@@

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{M-eqn:var} of the main text. The 
  entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
  parameters were relatively insensitive to the priors. In order to 
  maximally automate the IHMM procedure, we attempted to parameterize the
  prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
  be chosen such that the mean level of each state lies within a region of 
  reasonable probability of the prior (see Figure~\ref{fig:prior_guesses}).
  In each dimension, we defined the prior mean to lie halfway between the 
  maximum and minimum of each trajectory dimension. To parameterize the 
  prior's variance in each dimension, we defined the maximum and minimum to 
  be 2 standard deviations from the prior mean. Although this approach has 
  worked quite well for the data in this work, it is important to check the 
  results to determine whether further adjustments to the prior might be needed.
%  In Figure TBD, we show the result of a parameterization where the prior
%  parameters of $c$ were poorly chosen. %TODO

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{bayesian_A.pdf}
  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
  \end{subfigure}
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{agglomerative_A.pdf}
  \caption{Agglomerative Clustering}\label{fig:agglomerative_A}
  \end{subfigure}
  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
  Gaussian mixture modeling. In the plots above we show the results of clustering the
  diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
  since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
  clusters and ensures that all states within each cluster have similar parameters.
  }\label{fig:clustering_choice}
  \end{figure}

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_MET.pdf}
  \caption{methanol}\label{fig:silhouette_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_URE.pdf}
  \caption{urea}\label{fig:silhouette_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_GCL.pdf}
  \caption{ethylene glycol}\label{fig:silhouette_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_ACH.pdf}
  \caption{acetic acid}\label{fig:silhouette_ACH}
  \end{subfigure}
  \caption{We used the silhouette score test in order to quantitatively
  inform our decision on the numbrer of clusters. Silhouette scores 
  closer to one indicate good clustering. The crosses on the plot indicate
  our choice in number of clusters after careful consideration of the
  silhouette scores in conjunction with qualitative examination of the clusters
  formed by the choice. Although the test often
  favors fewer states, we elected to use an intermediate number of states in 
  the cases of $A$ and $\Sigma$ because choosing 2--3 clusters 
  insufficiently separates the dynamical modes. }\label{fig:silhouette}
  \end{figure}

\end{document}

>>>>

\chapter{Supporting Information to Chapter 5}\label{SI:ch5}

@@

  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the figures
  that follow, we graphically illustrate the procedure which is described in detail in
  Section~\ref{method:IHMM} of Chapter 5.

@@

  \begin{figure}
    \centering
	\begin{subfigure}{0.75\textwidth}
		\includegraphics[width=\textwidth]{xyz_hmm.pdf}
		\caption{}\label{fig:xyz_hmm}
	\end{subfigure}  	
	\begin{subfigure}{0.75\textwidth}
		\includegraphics[width=\textwidth]{rz_hmm.pdf}
		\caption{}\label{fig:rz_hmm}
	\end{subfigure}  
	\begin{subfigure}{0.75\textwidth}
		\includegraphics[width=\textwidth]{zeroed_hmm.pdf}
		\caption{}\label{fig:zeroed_hmm}
	\end{subfigure}  
	\caption{IHMM parameterization is a multi-step procedure. In the above plots, distinct colors
	correspond to distinct state behavior. (a) First we parameterize the trajectories in terms of
	the $x$, $y$, $z$ solute center-of-mass coordinates with the $x$ and $y$ coordinates relative
	to the nearest pore center (b) Next, we convert the $x$ and $y$ 	
	coordinates to radial coordinates, $r$, then fix the state sequence and use the inference 
	component of the IHMM in order to estimate the parameters in terms of $r$ and $z$. Note that
	the segment colors in (b) are the same as (a) because we fixed the state sequence.
	(c) After clustering the VAR parameters and reassigning the state sequence so that segments 
	which belong to the same cluster are labeled the same across all solute trajectories, we subtract
	the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory, and then fix the clustered state sequence to infer the parameters of each clustered 
  	state, assuming a mean of zero for all states. Note that the colors are no longer aligned with 
  	figures (a) and (b) because the states are relabeled in terms of their clusters. There are
  	also less states in this single trajectory.
	}\label{fig:hmm_demo}
  \end{figure}

@@

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. The 
  entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
  parameters were relatively insensitive to the priors. In order to 
  maximally automate the IHMM procedure, we attempted to parameterize the
  prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
  be chosen such that the mean level of each state lies within a region of 
  reasonable probability of the prior (see Figure~\ref{fig:prior_guesses}).
  In each dimension, we defined the prior mean to lie halfway between the 
  maximum and minimum of each trajectory dimension. To parameterize the 
  prior's variance in each dimension, we defined the maximum and minimum to 
  be 2 standard deviations from the prior mean. Although this approach has 
  worked quite well for the data in this work, it is important to check the 
  results to determine whether further adjustments to the prior might be needed.
%  In Figure TBD, we show the result of a parameterization where the prior
%  parameters of $c$ were poorly chosen. %TODO

@@

  \begin{figure}[h!]
  \centering
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{bayesian_A.pdf}
  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
  \end{subfigure}
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{agglomerative_A.pdf}
  \caption{Agglomerative Clustering}\label{fig:agglomerative_A}
  \end{subfigure}
  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
  Gaussian mixture modeling. In the plots above we show the results of clustering the
  diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
  since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
  clusters and ensures that all states within each cluster have similar parameters.
  }\label{fig:clustering_choice}
  \end{figure}

@@

  \begin{figure}[h!]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_MET.pdf}
  \caption{methanol}\label{fig:silhouette_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_URE.pdf}
  \caption{urea}\label{fig:silhouette_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_GCL.pdf}
  \caption{ethylene glycol}\label{fig:silhouette_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_ACH.pdf}
  \caption{acetic acid}\label{fig:silhouette_ACH}
  \end{subfigure}
  \caption{We used the silhouette score test in order to quantitatively
  inform our decision on the number of clusters. Silhouette scores 
  closer to one indicate good clustering. The crosses on the plot indicate
  our choice in number of clusters after careful consideration of the
  silhouette scores in conjunction with qualitative examination of the clusters
  formed by the choice. Although the test often
  favors fewer states, we elected to use an intermediate number of states in 
  the cases of $A$ and $\Sigma$ because choosing 2--3 clusters 
  insufficiently separates the dynamical modes. }\label{fig:silhouette}
  \end{figure}

### 2020-04-27 Ben_Manuscripts/thesis/intro.tex
Added missing intro figs
spell checking and mod to usage of subdiffusion

8\chapter{Introduction}\label{chapter:intro}

@@

  Although there has been considerable focus on creating membranes with high
  permeabilities, there is a case to be made that shifting the focus to membrane
  selectivity may offer a more effective route towards lowering the cost of 
  membrane separations.~\cite{werber_materials_2016} Increasing permeabilities
  beyond those already achieved may have only a small effect on energy 
  requirements and capital costs. Cohen-Tanugi \textit{et al.} calculated that 
  a theoretical tripling of membrane permeability would only reduce energy 
  consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
  Perhaps the most aggravating influence on energy consumption is the practical
  need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
  Additionally, many membranes are not suited for high purity separations
  of small neutral species which necessitates chemical and capital costs for
  post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
  Addressing these problems with highly selective separations may lead to 
  more signficant advances.~\cite{deshmukh_desalination_2015}

@@

  \textit{Desalination}: Creating potable water from seawater or brackish water is of 
  paramount importance in water-scarce areas. It is estimated that by 2025, 1.8 
  billion people may live in water-stressed regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
  Membrane deslination via RO and thermal muli-stage flash distillation are 
  both widely used processes for creating potable water in these regions.~\cite{fritzmann_state---art_2007}
  Compared with thermal distillation techniques, RO has been shown to 
  be more environmentally friendly and economical due to its lower energy
  requirements.\cite{morton_environmental_1997} However, thermal techniques are still
  preferred where excess waste heat or cheap thermal energy is available, such as
  cogeneration plants.\cite{bhojwani_technology_2019}

  \textit{Organic Micropollutants}: Municipal and industrial wastewaters are contaminated
  by harmful micropollutants, which can have adverse effects on human health even at low 
  concentrations.\cite{schwarzenbach_challenge_2006} Micropollutants include pharmaceuticals,
  personal care products, hormones, pesticides and industrial chemicals which find their way
  into our drinking water supply.~\cite{barbosa_occurrence_2016} Sources of micropollutants
  incude industrial wastewater, agricultural runoff, landfill leachates and domestic 
  effluents.~\cite{mompelat_occurrence_2009} Unfortunately, most waste water treatment 
  plants are not designed for complete removal of these contaminants.~\cite{tijani_review_2013}
  There is a need for a new generation of membranes that can better target specific molecules.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/graphene.pdf}
  \caption{graphene}\label{fig:graphene}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/cnt.png}
  \caption{carbon nanotube}\label{fig:cnt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth} % https://america.iza-structure.org/IZA-SC/framework_3d.php?STC=LTA
  \includegraphics[width=\textwidth]{figs/zeolite.png}
  \caption{zeolite, ZK-4}\label{fig:zeolite}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/mof.png}
  \caption{metal organic framework, MOF-5}\label{fig:mof}
  \end{subfigure}
  \caption{(a) Pristine graphene (left) and graphene oxide (right) are atomically thick,
  offering the potential for high permeabilities. (b) Carbon nanotubes exhibit extemely
  fast water transport due to their hydrophobic interiors. (c) Zeolites, like ZK-4 
  shown here, possess cage-like structures that can trap solutes. (d) Metal organic
  frameworks are flexible, porous structures capable of selective adsorption. }\label{fig:nanostructured_materials}
  \end{figure}

@@

  \textit{Zeolites}: Zeolite membranes offer the potential for permeabilities 
  comparable to ultrafiltration, with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
  Zeolites have highly uniform nm-sized crystalline structures with cage-like
  cavities that allow movement and trapping of small solutes. The crystalline 
  frameworks are typically formed by networks of silicon and/or aluminum each 
  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
  One can replace the silicon and aluminum atoms via ion exchange in order
  to control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}

  A number of studies have tested the permeability and sodium salt rejection
  of various zeolite membranes, however their high permeabilities typcially come
  at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
  Zeolite-coated ceramic membranes have shown the most promise for RO applications
  because of their mechanical stability under high applied pressure and chemical
  stability for withstanding disinfectants.~\cite{pendergast_review_2011}
  Unfortunately, zeolites are prone to defects in their crystalline structure which 
  would require substantial modification to the traditional synthesis procedures
  in order to fix.~\cite{kumakiri_application_2000}

@@

  Under the right conditions, the shape and amphiphilic character of liquid 
  crystal monomers drives their self-assembling into ordered nanostructures with
  uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
  As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
  (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
  bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
  The tails have vinyl groups which can be cross-linked for mechanical strength.

@@

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/lc_phases.pdf}
  \caption{The amphiphilic character of liquid crystal monomers drives their
  self-assembly into various nanostructured phases with uniform sized pores. 
  The hydrophilic components of the monomers line the aqueous pores, offering
  potential for selective interactions with passing solutes. The monomer on 
  the top left will form the inverted hexagonal (H\textsubscript{II})
  phase which is composed of aligned cylindrical pores packed in a hexagonal 
  array. This geometry is theoretically ideal for high throughput transport. 
  The monomer on the right will for the type I bicontinuous cubic phase
  (Q\textsubscript{I}) in either the Ia3d (gyroid) or Pn3m (diamond) space group.
  Although the Q\textsubscript{I} phase has a much more tortuous network of 
  pores than the H\textsubscript{II}, which should lower its relative permeabily,
  its synthesis is much more practical because it does not require alignment of
  the nanostructured mesophases.
  }\label{fig:lc_phases}
  \end{figure}

@@

    	  After gaining a detailed picture of the nanopore structure, we can 
    	  feel confident that solutes in this system will experience qualitatively 
    	  similar interactions which are present in a real system. We create independent
    	  systems for each of 20 small polar solutes and observe transport mechanisms
    	  whose dominance is dependent on solute chemical functionality. We characterize
    	  three different trapping mechanisms which lead to subdiffusive transport behavior.

@@

		  Using our qualitative understanding of the dominant trapping mechanisms,
    	  we develop stochastic time series models which we can use to mimic solute dynamic
    	  behavior on time scales orders of magnitude longer than our simulations. 
    	  We attempt to reproduce both quantitative and qualitative solute trajectory
    	  behavior on MD simulation-length timescales. We then show how we can use our 
    	  most promsiing model in order to connect microscopic transport to macroscopic
    	  flux and selectivity.

>>>>

\chapter{Introduction}\label{chapter:intro}

@@

  Although there has been considerable focus on creating membranes with high
  permeabilities, there is a case to be made that shifting the focus to membrane
  selectivity may offer a more effective route towards lowering the cost of 
  membrane separations.~\cite{werber_materials_2016} Increasing permeabilities
  beyond those already achieved may have only a small effect on energy 
  requirements and capital costs. Cohen-Tanugi \textit{et al.} calculated that 
  a theoretical tripling of membrane permeability would only reduce energy 
  consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
  Perhaps the most aggravating influence on energy consumption is the practical
  need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
  Additionally, many membranes are not suited for high purity separations
  of small neutral species which necessitates chemical and capital costs for
  post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
  Addressing these problems with highly selective separations may lead to 
  more significant advances.~\cite{deshmukh_desalination_2015}

@@

  \textit{Desalination}: Creating potable water from seawater or brackish water is of 
  paramount importance in water-scarce areas. It is estimated that by 2025, 1.8 
  billion people may live in water-stressed regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
  Membrane desalination via RO and thermal multi-stage flash distillation are 
  both widely used processes for creating potable water in these regions.~\cite{fritzmann_state---art_2007}
  Compared with thermal distillation techniques, RO has been shown to 
  be more environmentally friendly and economical due to its lower energy
  requirements.\cite{morton_environmental_1997} However, thermal techniques are still
  preferred where excess waste heat or cheap thermal energy is available, such as
  cogeneration plants.\cite{bhojwani_technology_2019}

  \textit{Organic Micropollutants}: Municipal and industrial wastewaters are contaminated
  by harmful micropollutants, which can have adverse effects on human health even at low 
  concentrations.\cite{schwarzenbach_challenge_2006} Micropollutants include pharmaceuticals,
  personal care products, hormones, pesticides and industrial chemicals which find their way
  into our drinking water supply.~\cite{barbosa_occurrence_2016} Sources of micropollutants
  include industrial wastewater, agricultural runoff, landfill leachate and domestic 
  effluents.~\cite{mompelat_occurrence_2009} Unfortunately, most waste water treatment 
  plants are not designed for complete removal of these contaminants.~\cite{tijani_review_2013}
  There is a need for a new generation of membranes that can better target specific molecules.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/graphene.pdf}
  \caption{graphene}\label{fig:graphene}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/cnt.png}
  \caption{carbon nanotube}\label{fig:cnt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth} % https://america.iza-structure.org/IZA-SC/framework_3d.php?STC=LTA
  \includegraphics[width=\textwidth]{figs/zeolite.png}
  \caption{zeolite, ZK-4}\label{fig:zeolite}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{figs/mof.png}
  \caption{metal organic framework, MOF-5}\label{fig:mof}
  \end{subfigure}
  \caption{(a) Pristine graphene (left) and graphene oxide (right) are atomically thick,
  offering the potential for high permeabilities. (b) Carbon nanotubes exhibit extremely
  fast water transport due to their hydrophobic interiors. (c) Zeolites, like ZK-4 
  shown here, possess cage-like structures that can trap solutes. (d) Metal organic
  frameworks are flexible, porous structures capable of selective adsorption. }\label{fig:nanostructured_materials}
  \end{figure}

@@

  \textit{Zeolites}: Zeolite membranes offer the potential for permeabilities 
  comparable to ultrafiltration, with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
  Zeolites have highly uniform nm-sized crystalline structures with cage-like
  cavities that allow movement and trapping of small solutes. The crystalline 
  frameworks are typically formed by networks of silicon and/or aluminum each 
  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
  One can replace the silicon and aluminum atoms via ion exchange in order
  to control the size of the cavities and hence its molecular-sieving properties.~\cite{li_novel_2007}

  A number of studies have tested the permeability and sodium salt rejection
  of various zeolite membranes, however their high permeabilities typically come
  at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
  Zeolite-coated ceramic membranes have shown the most promise for RO applications
  because of their mechanical stability under high applied pressure and chemical
  stability for withstanding disinfectants.~\cite{pendergast_review_2011}
  Unfortunately, zeolites are prone to defects in their crystalline structure which 
  would require substantial modification to the traditional synthesis procedures
  in order to fix.~\cite{kumakiri_application_2000}

@@

  Under the right conditions, the shape and amphiphilic character of liquid 
  crystal monomers drives their self-assembling into ordered nanostructures with
  uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
  As shown in Figure~\ref{fig:lc_phases}, monomer 1 will form the inverted hexagonal phase 
  (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
  bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
  The tails have vinyl groups which can be cross-linked for mechanical strength.

@@

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/lc_phases.pdf}
  \caption{The amphiphilic character of liquid crystal monomers drives their
  self-assembly into various nanostructured phases with uniform sized pores. 
  The hydrophilic components of the monomers line the aqueous pores, offering
  potential for selective interactions with passing solutes. The monomer on 
  the top left will form the inverted hexagonal (H\textsubscript{II})
  phase which is composed of aligned cylindrical pores packed in a hexagonal 
  array. This geometry is theoretically ideal for high throughput transport. 
  The monomer on the right will for the type I bicontinuous cubic phase
  (Q\textsubscript{I}) in either the Ia3d (gyroid) or Pn3m (diamond) space group.
  Although the Q\textsubscript{I} phase has a much more tortuous network of 
  pores than the H\textsubscript{II}, which should lower its relative permeability,
  its synthesis is much more practical because it does not require alignment of
  the nanostructured mesophases.
  }\label{fig:lc_phases}
  \end{figure}

@@

    	  After gaining a detailed picture of the nanopore structure, we can 
    	  feel confident that solutes in this system will experience qualitatively 
    	  similar interactions which are present in a real system. We create independent
    	  systems for each of 20 small polar solutes and observe transport mechanisms
    	  whose dominance is dependent on solute chemical functionality. We characterize
    	  three different trapping mechanisms which lead to subdiffusive transport behavior
    	  %BJCF: added
    	  on the timescales of our simulations.

@@

		  Using our qualitative understanding of the dominant trapping mechanisms,
    	  we develop stochastic time series models which we can use to mimic solute dynamic
    	  behavior on time scales orders of magnitude longer than our simulations. 
    	  We attempt to reproduce both quantitative and qualitative solute trajectory
    	  behavior on MD simulation-length timescales. We then show how we can use our 
    	  most promising model in order to connect microscopic transport to macroscopic
    	  flux and selectivity.
